A holographic approach to the six-dimensional superconformal index

### 2022-10-13 fivebranes/index.tex
section 3

Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
\[
\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong
\]
Thus, we have a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$. In particular, the result is local on $R_{>0}\times Z$.

@@

>>>>

We denote the resulting infinite dimensional vector space.
%Moreover, the deformation retraction along the fibers $(R\times \C^{2})_{(t,p)}- 0 \to S^{4}_{(t,p)}$ induces a quasi-isomorphism
%\[
%\left (\Gamma \left (S^{4}_{(t,p)}, \cA^{\bullet}_{\mathring M/\R_{>0}\times Z}(L) \right ) ; \thfd_{0}\right) \cong
%\]
Thus, we have a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$. In particular, the result is local on $R_{>0}\times Z$.

@@

\surya{...}
